%-------------------------
% Resume in Latex
% Author : Matty
% Based on: https://github.com/jakegut/resume (which was itself based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------


\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape Divyansh Singh} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/DivyanshAfk}{\underline{github.com/DivyanshAfk}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/divyansh-singh-739960232}{\underline{linkedin.com/divyanshsingh}} $  $
    \faIcon{envelope}
    \href{mailto:divyanshsiit@gmail.com}
    {\underline{divyanshsiit@gmail.com}}
\end{center}
% -------------------- Career Objective --------------------

\section{Career Objective}
\resumeSubHeadingListStart
{To leverage my skills in software engineering and to contribute meaningfully, driving innovation and achieving excellence. Seeking opportunities to continually learn, grow, and make a positive impact within a dynamic and collaborative work environment.}
\resumeSubHeadingListEnd

% -------------------- EDUCATION --------------------

\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Birla Institute of Technology, Mesra}{May 2025}
      {Bachelor of Technology in Electrical and Electronics Engineering, GPA: 8.05}{}
      
    \resumeSubheading
      {Aklank Day Boarding Cum Reidential School}{2019-2021}
      {Senior Secondary High School, CBSE Board: 91\%}{}

      \resumeSubheading
      {Stella Maris Convent School School}{2018-2019}
      {High School, CBSE Board: 96.6\%}{}

    

  \resumeSubHeadingListEnd
  
  

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: C/C++, Python, Java, JavaScript/TypeScript, HTML/CSS, Motoko} \\
     
     \textbf{Tools}{: Git/GitHub, Unix Shell, Webpack, VS Code, IntelliJ CLion/PyCharm/IDEA, Atom}\\
     
     \textbf{Frameworks}{: React, Node.js, Tailwind, Bootsrap,OAuth, Web3} \\
     
     % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
     
    }}
 \end{itemize}

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Paytm Clone App} $|$ \footnotesize\emph{MongoDB, React.Js, ExpressJs, NodeJs, Git, JWT Tokens, VS Code}}{}
        \resumeItemListStart
            \resumeItem{This project is a clone of the Paytm app, built using MongoDB, Express, and Node.js, with authentication handled by Zod and JWT.}
            \resumeItem{Utilizes the MERN stack - MongoDB for the database, Express for the server framework, and Node.js for the back-end runtime environment}
            \resumeItem{Employs JSON Web Tokens (JWT) for secure authentication, ensuring protected access to user-specific features and data.}
             \resumeItem{ Replicates key Paytm features such as user registration, login, digital payments, and wallet management, providing a seamless user experience.}
          \resumeItemListEnd
    
        \resumeProjectHeading
        {\textbf{Real Time Weather Application} $|$ \footnotesize\emph{Javascript, HTML/CSS, EJS, API, Git, VS Code}}{}
        \resumeItemListStart
            \resumeItem{Real Time Weather Application}
            \resumeItem{Developed a real-time weather app using OpenWeatherMap APIs, offering users accurate weather updates globally. The app displayed current conditions, hourly forecasts, and alerts.}
            \resumeItem{Handles API requests efficiently, parsed responses, and featured error handling for reliability. The result was a user-friendly tool for accessing precise weather information anytime, anywhere}
            
          \resumeItemListEnd
          
          
    \resumeSubHeadingListEnd

% -------------------- Co-Curricular Activites --------------------
\section{Co Curricular Activities}
  \resumeSubHeadingListStart

          \resumeProjectHeading
          {\textbf{Village Education Programme} $|$ \footnotesize\emph{Volunteer}\vspace{8pt}}{Aug. 2022 -- May.2023}
          {\small{taught Unprivileged Children in neighbouring villages twice a week.}}

          \resumeProjectHeading
          {\textbf{National Service Scheme}\vspace{8pt} $|$ \footnotesize\emph{Volunteer}}{2021 -- 2023}
          \small{Routinely participated in cleanliness and awareness drives and actively donating blood. }

          \resumeProjectHeading
          {\textbf{Leetcode}  \footnotesize\emph{}\vspace{8pt}}{2021 -- Present}
          {\small{Maintained a consistent streak on leetcode, demonstrating strong commitment to continuous learning and problem-solving skills in algorithmic and data structure challenges.}}
\resumeSubHeadingListEnd 
% ------------ Extra-Curricular Activites ------------------ 
        \section{Extra-Curricular Activites}
          \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{Sports}\vspace{8pt}}{2013 -- present}
          {\small{Represented Hostel cricket team as the captain.}}

    \resumeSubHeadingListEnd 

\end{document}
